\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-30 ASApaper/paper-child.Rnw
couple of points for discussion

>>>>

\hh{Best results: visual detection/ power analysis, a lot of variability in goodness of fit and significance tests. BUT: visualizations show that a decision of significance/ goodness of fit are not as clear cut as the traditional tests want us to believe.

Limitations: 
\begin{itemize}
\item number of null plots: null plots are representatives of the null distribution of all possible node-link diagrams of data sampled from the null model. Here, the number of null plots is  reduced to five, which increases the variability seen from a single lineup dramatically and unfortunately leads to different conclusions.
\item ability to generalize: the lineups are made for only one test case - it is not clear, whether and how far, power results transfer to other situations with different number of actors and different edge density.
\end{itemize}}
